# scratch area


```{r ,include=FALSE}
library(Rose)
library(ggplot2)
library(plotly)
library(knitr)
require(tikzDevice)
df <- data.frame(x = 1:5, y = 1:5)
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knit handle the plot
myplotly(ggplot())
```


We have the identity
\begin{gather}
	 c(t)=\int_{E_0}^{\infty}dE \rho(E) e^{-Et}
	=\cancel{\rho\frac{e^{-Et}}{-t}\bigg|_{E_0}^{\infty}} -\int_{E_0}^{\infty}dE \rho'(E)\frac{e^{-Et}}{-t}
\end{gather}
thus using as a base $\tilde b_t(E)=\frac{e^{-Et}}{t}$ to approximate $\Delta$ using the HLT we can compute the convolution  $\int\rho'\Delta$
\begin{gather}
	\sum_t g_tc(t)=\int_{E_0}^{\infty}dE \rho'(E) \sum_t g_t\frac{e^{-Et}}{t}=
	\int_{E_0}^{\infty}dE \rho'(E) \tilde \Delta(E)
	\\=\cancel{\rho \Delta\bigg|_{E_0}^{\infty} }-\int_{E_0}^{\infty}dE \rho(E) \tilde \Delta'(E)\,.
\end{gather}
So if we use as base $\tilde b_t(E)=\frac{e^{-Et}}{t}$ to approximate $\Delta$ with the HLT 
we can compute the convolution $-\int\rho\Delta'$.
For $Z_0$ the kernel function is 
\begin{gather}
  \theta_0(\omega-\omega_0)=\frac{c}{1+e^{\frac{\omega-\omega_0}{\sigma}}}\,,\\
  -\int \theta_0(\omega-\omega_0)=
  c\left[\sigma \log\left(e^{\frac{\omega_0}{\sigma}}+e^{\frac{\omega}{\sigma}}\,. \right)-\omega\right]
\end{gather}


- One could also try $-\int \theta_0(\omega-\omega_0)\approx-(\omega-\omega_0)\theta_0(\omega-\omega_0)$

- We could iterate the procedure and use as base $b_t''=\frac{e^{-Et}}{t^2}$ to     approximate $\int \int\Delta$
$$\int\int\Delta=\int\int \theta_0(\omega-\omega_0)\approx \frac{1}{2} (\omega-\omega_0)^2\theta_0(\omega-\omega_0)$$

- We try a different function that approach the $\theta$, the algebraic function
$$
  \theta_0^{algebraic}=\frac{c}{2}\left( \frac{x}{\sqrt{1+x^2}}+1\right)\,, \quad x=\frac{\omega_0-\omega}{\sigma}
$$

```{r,results='asis', echo=FALSE}
dir<-"/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/"
ths<- c("3")
```


## Stability



```{r, echo=FALSE, results='asis', warning=FALSE}

Zs<- c("Z0")
for (Z in Zs){
cat("\n## ",Z,"\n\n")
  
for (i in seq_along(ths) ){

df<-NULL


fileA<-paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th",ths[i],"_t78_62.dat_HLT_AoverB")
mtA<-read_df(fileA)
all_obsA<- get_all_corr(mtA)
dfA<-get_block(string =paste0("HLT_",Z,"-bt-sig0.000500-alpha0.00"),
                    all_obs=all_obsA,mt=mtA,df = NULL,
                   log = FALSE, number = NULL,nudge = 0,
                    print_res = TRUE,logx=10,ix=11,
                    iy=6,ierr=7,ifit=9,ierrfit=10,
                    iplateau = 1,
                   rename="$\\theta_0(\\omega-\\omega_0)$"
                   )
# dfA<-get_block(string =paste0("HLT_",Z,"-deriv-bt-sig0.000500-alpha0.00"),
#                     all_obs=all_obsA,mt=mtA,df = dfA,
#                    log = FALSE, number = NULL,nudge = 0,
#                     print_res = FALSE,logx=10,ix=11, iy=6,ierr=7,ifit=9,ierrfit=10,
#                     iplateau = 1
#                    )
dfA<-get_block(string =paste0("HLT_",Z,"-part-bt-sig0.000500-alpha0.00"),
                    all_obs=all_obsA,mt=mtA,df = dfA,
                   log = FALSE, number = NULL,nudge = 0,
                    print_res = TRUE,logx=10,ix=11,
                    iy=6,ierr=7,ifit=9,ierrfit=10,
                    iplateau = 1,
                    rename="$-\\int \\theta_0(\\omega-\\omega_0)$"
                   )

dfA<-get_block(string =paste0("HLT_",Z,"-part-bt-k2-sig0.000500-alpha0.00"),
                    all_obs=all_obsA,mt=mtA,df = dfA,
                   log = FALSE, number = NULL,nudge = 0,
                    print_res = TRUE,logx=10,ix=11,
                    iy=6,ierr=7,ifit=9,ierrfit=10,
                    iplateau = 1,
                    rename="$-(\\omega-\\omega_0)\\theta_0(\\omega-\\omega_0)$"
                   )
dfA<-get_block(string =paste0("HLT_",Z,"-part2-bt-k2-sig0.000500-alpha0.00"),
                    all_obs=all_obsA,mt=mtA,df = dfA,
                   log = FALSE, number = NULL,nudge = 0,
                    print_res = TRUE,logx=10,ix=11,
                    iy=6,ierr=7,ifit=9,ierrfit=10,
                    iplateau = 1,
                    rename="$0.5(\\omega-\\omega_0)^2\\theta_0(\\omega-\\omega_0)$"
                   )
dfA<-get_block(string =paste0("HLT_",Z,"-algebraic_th-sig0.000500-alpha0.00"),
                    all_obs=all_obsA,mt=mtA,df = dfA,
                   log = FALSE, number = NULL,nudge = 0,
                    print_res = TRUE,logx=10,ix=11,
                    iy=6,ierr=7,ifit=9,ierrfit=10,
                    iplateau = 1,
                    rename="$\\theta_0^{algebraic}(\\omega-\\omega_0)$"
                   )


dfA$x<-dfA$x-log10(dfA[,4])# A/A0
dfA$xfit<-dfA$xfit-log10(dfA[,4])# A/A0
dfA$tmin<-dfA$tmin-log10(dfA[,4])# A/A0
dfA$tmax<-dfA$tmax-log10(dfA[,4])# A/A0
gg<- plot_df_corr_ggplot(dfA,width = 0.02)
fig<- myplotly(gg,"","$\\log_{10}(A/A_0)\\big|_{ref}$", paste0("$\\rho(\\theta=",ths[i],")$"), to_print=TRUE, legend_position = c(0.6,0.95) )


}
}
```




```{r, echo=FALSE, results='asis', warning=FALSE}

Zs<- c("Z0")
Z<-Zs[1]

cat("\n## ",Z,"\n\n")
 
  
df<-NULL
###################### MG

mt1<-read_df(paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_HLT_kernel"))
all_obs<- get_all_corr(mt1)
df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-bt-sig0.000500-alpha0.00_lam33554432"),
                    all_obs=all_obs,mt=mt1,df = NULL,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )


df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-bt-sig0.000500-alpha0.00_lam1024"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )

df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-bt-sig0.000500-alpha0.00_lam32"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )


tmp<-data.frame("omega"=df1$x, "K"=df1$y, "Kb"=df1$fit, 
                 "label"=paste0(df1$label)
                )
df<-rbind(df,tmp)
################ plot
gg<-myggplot(shape = FALSE,fill = FALSE)
gg<-gg + geom_line(aes(x=df$omega  , y=df$Kb,
                       color=forcats::fct_inorder(paste0("K-",df$label))
                       ),linetype="dashed" )
gg<-gg + geom_line(aes(x=df$omega  , y=df$K,
                 color="$\\theta_0(\\omega-\\omega_0)$"),
                 linetype="solid")
# gg<-gg+scale_color_discrete(limits=df$label)
# gg<-gg + geom_line(aes(x=df$omega  , y=df$K-df$Kb,
#                        color=paste0("diff-",df$label)
#                        ),linetype="dotted")
fig<- myplotly(gg,"","$\\omega$", "Kernel", to_print=TRUE , legend_position = c(0.5,0.95),legend_title = "")


```



```{r, echo=FALSE, results='asis', warning=FALSE}

Zs<- c("Z0")
Z<-Zs[1]

cat("\n## ",Z,"\n\n")
 
  
df<-NULL
###################### MG

mt1<-read_df(paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_HLT_kernel"))
all_obs<- get_all_corr(mt1)


df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-part-bt-sig0.000500-alpha0.00_lam33554432"),
                    all_obs=all_obs,mt=mt1,df = NULL,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )
df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-part-bt-sig0.000500-alpha0.00_lam1024"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )
df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-part-bt-sig0.000500-alpha0.00_lam32"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )


tmp<-data.frame("omega"=df1$x, "K"=df1$y, "Kb"=df1$fit, 
                 "label"=paste0(df1$label)
                )
df<-rbind(df,tmp)

################ plot
gg<-myggplot(shape = FALSE,fill = FALSE)
gg<-gg + geom_line(aes(x=df$omega  , y=df$Kb,
                       color=forcats::fct_inorder(paste0("K-",df$label))
                       ),linetype="dashed" )
gg<-gg + geom_line(aes(x=df$omega  , y=df$K,
                 color="$-\\int \\theta_0(\\omega-\\omega_0)$"),
                   linetype="solid")
# gg<-gg + geom_line(aes(x=df$omega  , y=df$K-df$Kb,
#                        color=paste0("diff-",df$label)
#                        ),linetype="dotted")
fig<- myplotly(gg,"","$\\omega$", "Kernel", to_print=TRUE , legend_position = c(0.5,0.95),legend_title = "")


```


```{r, echo=FALSE, results='asis', warning=FALSE}

Zs<- c("Z0")
Z<-Zs[1]

cat("\n## ",Z,"\n\n")
 
  
df<-NULL
###################### MG

mt1<-read_df(paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_HLT_kernel"))
all_obs<- get_all_corr(mt1)


df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-algebraic_th-sig0.120000-alpha0.00_lam33554432"),
                    all_obs=all_obs,mt=mt1,df = NULL,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )
df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-algebraic_th-sig0.120000-alpha0.00_lam1024"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )
df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-algebraic_th-sig0.120000-alpha0.00_lam32"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )


tmp<-data.frame("omega"=df1$x, "K"=df1$y, "Kb"=df1$fit, 
                 "label"=paste0(df1$label)
                )
df<-rbind(df,tmp)

################ plot
gg<-myggplot(shape = FALSE,fill = FALSE)
gg<-gg + geom_line(aes(x=df$omega  , y=df$Kb,
                       color=forcats::fct_inorder(paste0("K-",df$label))
                       ),linetype="dashed" )
gg<-gg + geom_line(aes(x=df$omega  , y=df$K,
                 color="$\\theta_0^{algebraic}(\\omega-\\omega_0)$"),
                   linetype="solid")
# gg<-gg + geom_line(aes(x=df$omega  , y=df$K-df$Kb,
#                        color=paste0("diff-",df$label)
#                        ),linetype="dotted")
fig<- myplotly(gg,"","$\\omega$", "Kernel", to_print=TRUE , legend_position = c(0.5,0.95),legend_title = "")


```


```{r, echo=FALSE, results='asis', warning=FALSE}

Zs<- c("Z0")
Z<-Zs[1]

cat("\n## ",Z,"\n\n")
 
  
df<-NULL
###################### MG

mt1<-read_df(paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_HLT_kernel"))
all_obs<- get_all_corr(mt1)


df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-part2-bt-k2-sig0.000500-alpha0.00_lam33554432"),
                    all_obs=all_obs,mt=mt1,df = NULL,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )
df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-part2-bt-k2-sig0.000500-alpha0.00_lam1024"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )
df1<-add_corr_to_df(
  string =paste0("HLT_",Z,"-part2-bt-k2-sig0.000500-alpha0.00_lam32"),
                    all_obs=all_obs,mt=mt1,df = df1,
                   log = FALSE, number = NULL,nudge = 0,
                   print_res = FALSE,
                   )


tmp<-data.frame("omega"=df1$x, "K"=df1$y, "Kb"=df1$fit, 
                 "label"=paste0(df1$label)
                )
df<-rbind(df,tmp)

################ plot
gg<-myggplot(shape = FALSE,fill = FALSE)
gg<-gg + geom_line(aes(x=df$omega  , y=df$Kb,
                       color=forcats::fct_inorder(paste0("K-",df$label))
                       ),linetype="dashed" )
gg<-gg + geom_line(aes(x=df$omega  , y=df$K,
                 color="$0.5(\\omega-\\omega_0)^2\\theta_0(\\omega-\\omega_0)$"),
                   linetype="solid")
# gg<-gg + geom_line(aes(x=df$omega  , y=df$K-df$Kb,
#                        color=paste0("diff-",df$label)
#                        ),linetype="dotted")
fig<- myplotly(gg,"","$\\omega$", "Kernel", to_print=TRUE , legend_position = c(0.5,0.95),legend_title = "")


```




## $\sigma$ extrapolation




```{r, echo=FALSE, results='asis', warning=FALSE}

#' plot the result of a fit
custom_plot_fit<-function(basename,var, data_type=NULL, gg=NULL, noribbon=FALSE, nudge=0){
  filed<-paste0(basename,"_fit_data.txt")
  df<- read.table(filed, header=FALSE, fill=TRUE)

  if (is.null(gg)) gg<- myggplot()
  idy<-ncol(df)-2
  # if (is.null(data_type))
  #   data_type<-as.factor(df[,idy+2])
  
  label<-as.factor(df[1,idy+2])
  if (!is.null(data_type))
    label<-data_type
  
  gg<-gg+  geom_pointrange(data=df,
                           mapping=aes(x=df[,1]+nudge , y=df[,idy],
                                       ymin=df[,idy]-df[,idy+1], ymax=df[,idy]+df[,idy+1],
                                       color=label,
                                       shape=label,
                                       fill=label  )
                           ,width=1e-4,size=1)

  datalist = list()
  lastr<-nrow(df)
  if(!noribbon){
    for (n in c(df[1,idy+2]:df[lastr,idy+2])){
  
      file=sprintf("%s_fit_out_n%d_%s.txt",basename,n,var)
      #browser()
      n1<-n+1
      datalist[[n1]]<- read.table(file, header=FALSE, fill=TRUE,
                                  col.names=c(paste0("x",n),paste0("fit",n),paste0("fiterr",n)))
      gg<-gg + geom_ribbon(data=datalist[[n1]],
                           mapping=aes_string(x=datalist[[n1]][,1] ,
                            ymin=datalist[[n1]][,2]-datalist[[n1]][,3],
                            ymax=datalist[[n1]][,2]+datalist[[n1]][,3],
                                              fill=as.factor(paste0("fit",label)),
                                              color=as.factor(paste0("fit",label)),
                                              shape=as.factor(paste0("fit",label)) ),
                           alpha=0.5 )
      gg<-gg + geom_line(data=datalist[[n1]],
                         mapping=aes_string(x=datalist[[n1]][,1] ,
                                            y=datalist[[n1]][,2],
                                            fill=as.factor(paste0("fit",label)),
                                              color=as.factor(paste0("fit",label)),
                                              shape=as.factor(paste0("fit",label)))
      )
    }
  }
  return(gg)
}

Zs<- c("Z0")
for (Z in Zs){
cat("\n## ",Z,"\n\n")
for (i in seq_along(ths) ){
  file<-paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_fit_HLT_",Z,"-sigma")
  gg<-custom_plot_fit(file,"sigma", "Z0" )



  file<-paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_fit_HLT_",Z,"-part-bt-k2-sigma")
  gg<-custom_plot_fit(file,"sigma", "$-(\\omega-\\omega_0)\\theta_0(\\omega-\\omega_0)$" , gg=gg,nudge = 0.001)


    file<-paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_fit_HLT_",Z,"-part2-bt-k2-sigma")
  gg<-custom_plot_fit(file,"sigma", "$0.5(\\omega-\\omega_0)^2\\theta_0(\\omega-\\omega_0)$" , gg=gg,nudge = 0.002)
  
    file<-paste0("/home/garofalo/analysis/heavy_quarks/data_Inc/test_Emax/out/cD211.054.96_th3_t78_62.dat_fit_HLT_",Z,"-algebraic_th-sigma")
  gg<-custom_plot_fit(file,"sigma", "$\\theta_0^{algebraic}(\\omega-\\omega_0)$" , gg=gg,nudge = 0.003)
  

  
  fig<- myplotly(gg,title,"$\\sigma$", paste0(Z,"-th",ths[i]),
                         to_print = TRUE, output="HTML", legend_position = c(0.8,0.9),
               legend_title = "") 
}
}
```

